Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-04-07 DGMM2025/paper.tex
tmpfix

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e.,\ \( [p, q] \subseteq \text{Star}(K)\)
    \end{definition}

@@

@@

            \Function{Translation}{$I$: Interval, L: list of Interval}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, L: list of Interval}
                \For{each interval $I$ in VectorI}
                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{L}}$
                \EndFor
                \State \Return \text{CurrentIResult}
            \EndFunction

            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
                \State $Visibility: \text{list of boolean} \gets \emptyset$
                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
                \For{each $V$ in $Vectors$}
                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
                    \For{every shift $tx, ty$ in $FigLattices$}
                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
                        \For{each $Lattice$ in $VStarLattice$}
                            \State \begin{varwidth}[t]{\linewidth}
                                       $CurrentIResult~\gets~MatchVector(CurrentIResult,$\par
                                       \hskip\algorithmicindent $Lattice.intervals,$\par
                                       \hskip\algorithmicindent $\text{FigLattices}[StartingPoint + Lattice.position])$
                            \end{varwidth}
                        \EndFor
                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
                    \EndFor
                \EndFor
                \State \Return $Visibility$
            \EndFunction

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals I and J, find $I \cup J$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection (\cup)}{\text{I, J}: list of Intervals}
                \State R \gets \emptyset
                \State k1, k2 = 0
                \While{k1 < I.nbIntervals \And k2 < J.nbIntervals}
                    \State i \gets I[k1]
                    \State j \gets J[k2]

                \EndWhile
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\usepackage{algc}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\)
    \end{definition}

@@

    \begin{definition}
        An interval $I$ is defined as the pair $[a,b], a \leq b, st. \forall a \leq n \leq b, n \in I$
    \end{definition}

@@

            \Function{Translation}{$I$: Interval, L: Intervals}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{MatchVector}{\text{CurrentIResult}: Intervals, VectorI: Intervals, L: Intervals}
                \For{each interval $I$ in VectorI}
                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{L}}$
                \EndFor
                \State \Return \text{CurrentIResult}
            \EndFunction

            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
                \State $Visibility: \text{vector of boolean} \gets \emptyset$
                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
                \For{each $V$ in $Vectors$}
                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
                    \For{every shift $tx, ty$ in $FigLattices$}
                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
                        \For{each $Lattice$ in $VStarLattice$}
                            \State \begin{varwidth}[t]{\linewidth}
                                       $CurrentIResult~\gets~MatchVector(CurrentIResult,$\par
                                       \hskip\algorithmicindent $Lattice.intervals,$\par
                                       \hskip\algorithmicindent $\text{FigLattices}[StartingPoint + Lattice.position])$
                            \end{varwidth}
                        \EndFor
                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
                    \EndFor
                \EndFor
                \State \Return $Visibility$
            \EndFunction

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals K and L, find $K \cup L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $cMin \gets max(a, c)$
                    \State $cMax \gets max(b, d)$
                    \If{$cMax < cMin$}
                        \State $R.append([cMin, cMax])$
                    \EndIf
                    \If{$a \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$c \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}
